\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{lpic}
\usepackage{amsthm}
\usepackage{float}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage[top=1in, bottom=1in, left=1.5in, right=1.5in]{geometry}
\usepackage{etoolbox}
\patchcmd{\quote}{\rightmargin}{\leftmargin 2em \rightmargin}{}{}
\allowdisplaybreaks

\usepackage{hyperref}
\hypersetup{pdfauthor={},pdftitle={determining the subgraphs of the curve graph},colorlinks=true,linkcolor=black,citecolor=black}


\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{notation}[theorem]{Notation}
\newtheorem*{theorem*}{Theorem}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}{Question}






%this has equations numbered within sections 1.1,1.2, ... 2.1,...
\numberwithin{equation}{section}


%-------------------------------------------
%       Begin Local Macros
%-------------------------------------------

\newcommand{\bC}{\mathbb{C}}
\newcommand{\bH}{\mathbb{H}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bQ}{\mathbb{Q}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bZ}{\mathbb{Z}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\Isom}{\mathrm{Isom}}
\newcommand{\PSL}{\mathrm{PSL}}
\newcommand{\Sub}{\mathrm{Sub}}
\newcommand{\Mod}{\mathrm{Mod}}        

%-------------------------------------------
%       End Local Macros
%-------------------------------------------

\linespread{1.1}

\title{Why can't I make the title look nice}
\author{Mujie Wang}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
	Future me will put some abstract here
\end{abstract}

\section{Introduction}



\section{Chab Chab}

Let $G$ be a Lie group, and $A_n$ and $A$ be its closed subgroups. We want to find a notion of convergence for closed subgroups. Chabauty topology gives such notion on the set $\Sub(G)$ of all closed subgroups of $G$. 

\begin{definition} \label{def:chabconv}
A sequence of closed subgroups $(A_n)$ converge to $A$ in Chabauty topology if 
\begin{enumerate}
	\item Any $x \in A$ is the limit of some sequence $(x_n)$ where $x_n \in A_n$
	\item Any accumulation point of a sequence $(x_n)$ where $x_n \in A_n$ lies in $A$. 
\end{enumerate}
\end{definition}

For this section, we let $G = \PSL_2(\bR)$. The group $G$ is the group of isometries acting on the upper half plane model of $\bH^2$ by fractional linear transformation. Using Chabauty topology, we are able to describe the shape of the collection of all closed subgroups of $G$, denoted by $S(G)$. To do so, We want to break $S(G)$ into pieces that we know the shape of, and then try to glue it back together by looking for convergence.

A sequence of cyclic subgroup generated by a hyperbolic isometry can converge to a cyclic subgroup generated by a parabolic isometry, as shown in the following example.  
\begin{example}
	Let $\xi_n = 1 + 1/n$,
	Consider 
		$$H_n = \dfrac12
			\begin{bmatrix} 
				\xi_n + \xi_n^{-1} & n(-\xi_n + \xi_n^{-1}) \\
				\dfrac1n(-\xi_n + \xi_n^{-1}) & \xi_n + \xi_n^{-1}
			\end{bmatrix}, \ \ 
		P = 
			\begin{bmatrix}
				1 & -1 \\ 0 & 1
			\end{bmatrix}
		$$
The sequence of subgroups $(\langle H_n \rangle)$ converges to the subgroup $\langle P \rangle$.

Here, $H_n$ is a hyperbolic isometry that fixes $n, -n \in \partial \bH^2$, leaves geodesic connecting $n, -n$ invariant, and travels along the geodesic by $2\ln(\xi_n)$; $P$ is a parabolic isometry that fixes $\infty \in \partial \bH^2$, and maps $z \mapsto z-1$.
\end{example}

\begin{proof}
It is not hard to show $H_n \to P$ as $n$ goes to $\infty$. However, as a noob in Chabauty topology, one might (for example I did) think we are done with this proof by showing that the sequence of generators converges to the generator. It suffices to show the following fact:
\begin{fact}
	$(H_n^{a_n})$ converges if and only if $(a_n)$ converges. Moreover, if $a_n \to a$, then $H_n^{a_n} \to P^a$. Here $a_n$ are integers
\end{fact}

It might be helpful to mention that 
$$H_n^{a_n} = \dfrac12
\begin{bmatrix}
	\xi_n^{a_n} + \xi_n^{-a_n} & n(-\xi_n^{a_n} + \xi_n^{-a_n}) \\
	\dfrac1n(-\xi_n^{a_n} + \xi_n^{-a_n}) & \xi_n^{a_n} + \xi_n^{-a_n}
\end{bmatrix}
$$
For top left and bottom right coefficients, 
$$ 
\xi_n^{a_n} + \xi_n^{-a_n} = \frac{(n+1)^{a_n}}{n^{a_n}} + \frac{n^{a_n}}{(n+1)^{a_n}} = \frac{(n+1)^{2a_n} + n^{2a_n}}{(n+1)^{a_n}n^{a_n}} \to 2
$$ because the leading terms of numerator and denominators have the same power $2a_n$. 

For the bottom left coefficient, 
\begin{align*}
\dfrac1n(-\xi_n^{a_n} + \xi_n^{-a_n}) &= \frac1n\left(-\frac{(n+1)^{a_n}}{n^{a_n}} + \frac{n^{a_n}}{(n+1)^{a_n}}\right) \\
&= \frac{-(n+1)^{2a_n} + n^{2a_n}}{(n+1)^{a_n}n^{a_n+1}} \to 0
\end{align*}
because the numerator is an at most $(2a_n-1)$ degree polynomial while the denominator is degree $(2a_n+1)$. These three coefficients converge for large $n$ no matter what $a_n$ is. 

Now here is where ``if and only if'' comes from. For the top right coefficient, 
\begin{align*}
n(-\xi_n^{a_n} + \xi_n^{-a_n}) &= n\left(-\frac{(n+1)^{a_n}}{n^{a_n}} + \frac{n^{a_n}}{(n+1)^{a_n}}\right) \\
&= \frac{n(-(n+1)^{2a_n} + n^{2a_n})}{(n+1)^{a_n}n^{a_n}}
\end{align*}
By binomial expansion, the leading term of the numerator is $2a_nn^{2a_n}$ and the leading term of the denominator is $n^{2a_n}$. So this term converges if and only if $a_n$ converges.
\end{proof}

[Include a picture here! ]

































\section{The plot thickens}


Jorgenson first discovered the following interesting phenomenon.

\begin{fact} \label{fact:Jorgenson}
	There exists a sequence of infinite cyclic groups $\langle H_n \rangle$, where $H_n$ is an isometry of hyperbolic type, such that the sequence converges to a subgroup isomorphic to $\mathbb{Z}^2$, whose generators are both parabolic isometries.
\end{fact}

In this section, we will construct one such sequence explicitly. We will use the upper half-plane model $\bC \times \bR^+$ for $\bH^3$. The isometry group $\cI^+(\bH^3) \cong \PSL_2(\bC)$ acts on the boundary $\overline\bC$ by fractional linear transformation. 

\section{Quotient things up}

\section{Convergence of the quotient}

\section{Closet of necessary backgrounds}

\bigskip

\bibliographystyle{alpha}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{OeSHP14}

\bibitem[PH]{PH}
Author names.
\newblock Article Titles.
\newblock {\em Journal Title},
  ??? some mysterious numbers.


\end{thebibliography}








\end{document}